---
date: "`r Sys.Date()`"
author: "NYSDEC SMAS"
title: "Dodge Creek at Portville, NY"
output: 
  officedown::rdocx_document:
     reference_docx: draft_template.docx
params:
    tox: FALSE
    study_name: "Dodge Creek at Portville, NY"
    year_input: 2021
    intro_file_name: "dodge_intro.csv"
    sites_file_name: "dodge_sites.csv"
    grouping_for_chem: site
    grouping_for_bap: site
    map_zoom: 15
    user: kareynol
    limit_to_nuts: TRUE
    data_package: FALSE
      
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
library(officedown)
library(officer)

fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)

study_name=params$study_name
tox=params$tox
intro_file_name=params$intro_file_name
sites_file_name=params$sites_file_name
year.input=params$year_input
#updated_sites_file_name=params$updated_sites_file_name
grouping_for_bap=params$grouping_for_bap
grouping_for_chem=params$grouping_for_chem
map_zoom=params$map_zoom
user=params$user
limit_to_nuts=params$limit_to_nuts
data_package=params$data_package

```


```{r message=FALSE,warning=FALSE,echo=FALSE}

year_input=params$year_input
source(here::here("rmd/r_scripts_raw/stayCALM_exceedances_updated.R"))
source(here::here("rmd/r_scripts_raw/functions.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_1_raw.R"))
year.input=params$year_input
source(here::here("rmd/r_scripts_raw/preprocessing_2_chemistry.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_3_bap.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_4_habitat.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_5_user_perception.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_6_tox.R"))
source(here::here("rmd/r_scripts_raw/appendices_and_data_package.R"))
```

<!---CHUNK_PAGEBREAK--->

<!---BLOCK_TOC--->
<!---BLOCK_TOC(style="Table Caption")--->
<!---BLOCK_TOC(style="Image Caption")--->


<!---CHUNK_PAGEBREAK--->


```{r gen_map, echo=FALSE,warning=FALSE,message=FALSE}
#figure this one out eventually, maybe have Andrea's map script.


```


# General
```{r child="child/section1_General.Rmd"}

```
\newpage

# Benthic Macroinvertebrate Community 
```{r child="child/section1B_BAP.Rmd"}

```
\newpage

# Biological Impairment Criteria

Biological assessment based on the macroinvertebrate community provide the ability to detect water quality problems that are intermittent, not detected, and/or underestimated by water chemistry sampling. Using biological sampling methods described above (SOP #208-21), criteria have been established for measuring significant biological impairment to resident aquatic life in flowing waters (Bode et al. 1995).  Using conditions upstream of a point source rather than reference condition (BAP >5.0) generate site-specific criteria and evaluates potential localized change in the macroinvertebrate community condition. 

To isolate water quality as the driver of potential impact to the macroinvertebrate community, several habitat features must be measured at both sampling locations and fall within documented habitat similarity requirements (Bode et al. 1995). These habitat features are routinely collected as part of macroinvertebrate community sampling (SOP #208-21) and include: substrate particle size (within 3 phi units), along with current speed, embeddedness, and canopy cover (all within 50%).


```{r tab.id= "hab", tab.cap="Habitat variable information collected at Dodge Creek (July 1, 2021) to evaluate potential influence of physical habitat on the macroinvertebrate community.", echo=FALSE, message=FALSE, warning=FALSE}

hab<-read.csv(here::here("data/Dodge_Creek_Field/hab.csv"),stringsAsFactors = FALSE)

hab<-hab %>% 
  rename(" "=X,
         "Phi Units"=Phi.Units,
         'Current (cm/s)'=Current..cm.s.,
         '% Embeddedness'=X..Embeddedness,
         '% Canopy'=X..Canopy)

table.f(hab,2,4)


```

*Determination of Significant Biological Impairment*

Significant biological impairment occurs when 1 or more of the biological metrics levels exceed the criteria for impairment designated in Table 4. If the mean of one or more biological metrics exceeds the criteria, a Student’s T test is run to determine statistical significance and confirm significant biological impairment. Biological metrics include Species Richness, Ephemeroptera, Plecoptera, Trichoptera, (EPT) Richness, Biotic Index, Species Dominance, Percent Model Affinity, and BAP. Table 4 indicates no exceedances of biological impairment criteria.


<!---BLOCK_LANDSCAPE_START--->


```{r tab.id= "richness", tab.cap="Sampling locations, replicate metric values and means, impairment criteria thresholds for means, and indication of biological impairment criteria exceedance.", echo=FALSE, message=FALSE, warning=FALSE}

richness<-read.csv(here::here("data/Dodge_Creek_Field/richness.csv"),stringsAsFactors = FALSE)

richness<-richness %>% 
  rename(" "=X,
         'Species Richness'=Species.Richness,
         'Species Dominance'=Species.Dominance,
         'EPT Richness'=EPT.Richness,
         'Biotic Index'=Biotic.Index,
         'Species Dominance'=Species.Dominance,
         'Percent Model Affinity'=Percent.Model.Affinity)

big_border=officer::fp_border(color="gray",width=1)

rich<-table.f(richness,2,4)
flextable::bg(rich, i=4, j = NULL, bg="grey", part = "body", source = j) %>% 
  flextable::bg(i=8, j = NULL, bg="grey", part = "body", source = j) %>% 
    flextable::bg(i=10, j = NULL, bg="grey", part = "body", source = j) %>% 
    flextable::bg( i=11, j = NULL, bg="grey54", part = "body", source = j) %>% 
  border_outer(part="all", border = big_border ) %>% 
  border_outer(part="header", border = big_border ) %>% 
  fit_to_width(max_width=10)
  
  

```

<!---BLOCK_LANDSCAPE_STOP--->

# Water Chemistry and Stream Discharge
```{r child="child/section1A_chemistry_stream_discharge.Rmd"}

```
\newpage

```{r child="child/section1E_tox.Rmd"}

if(params$tox){cat("# Sediment and Porewater Microtox® Analysis")}
```

\newpage

```{r child="child/appendices.Rmd"}

```

