---
date: "Report Date: `r Sys.Date()`"
author: "NYSDEC SMAS"
title: "Stream Survey Data Report"
output:
  officedown::rdocx_document:
    reference_docx: draft_template.docx
    tables:
      style: Table
      layout: autofit
      width: 0.75
      caption:
        style: Table Caption
        pre: 'Table '
        sep: '. '
    plots:
      style: Normal
      align: center
      caption:
        style: Image Caption
        pre: 'Figure '
        sep: '. '
params:
    tox: FALSE
    study_name: "Halfway Creek"
    year_input: 2019
    intro_file_name: "halfway_intro.csv"
    sites_file_name: "halfway_sites.csv"
    grouping_for_chem: site
    grouping_for_bap: site
    map_zoom: 12
    user: kareynol
    limit_to_nuts: TRUE
    data_package: TRUE
    lit_cited_file: "lit_cited.docx"
    map_file: "dodge_png.png"
      
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.cap = TRUE)
library(officedown)
library(officer)

fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)

rdocx_document(tables = list(
     style = "Table", layout = "autofit", width = 1,
   caption = list(
     style = "Table Caption", pre = "Table ", sep = ". "),
   conditional = list(
     first_row = TRUE, first_column = FALSE, last_row = FALSE,
     last_column = FALSE, no_hband = FALSE, no_vband = TRUE)))

rdocx_document(tables = list(
     style = "Image", layout = "autofit", width = 1,
   caption = list(
     style = "Image Caption", pre = "Figure ", sep = ". "),
   conditional = list(
     first_row = TRUE, first_column = FALSE, last_row = FALSE,
     last_column = FALSE, no_hband = FALSE, no_vband = TRUE)))


study_name=params$study_name
tox=params$tox
intro_file_name=params$intro_file_name
sites_file_name=params$sites_file_name
year.input=params$year_input
#updated_sites_file_name=params$updated_sites_file_name
grouping_for_bap=params$grouping_for_bap
grouping_for_chem=params$grouping_for_chem
map_zoom=params$map_zoom
user=params$user
limit_to_nuts=params$limit_to_nuts
data_package=params$data_package
lit_cited_file=params$lit_cited_file
map_file=params$map_file

```


```{r message=FALSE,warning=FALSE,echo=FALSE}

year_input=params$year_input
source(here::here("rmd/r_scripts_raw/stayCALM_exceedances_updated.R"))
source(here::here("rmd/r_scripts_raw/functions.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_1_raw.R"))
year.input=params$year_input
source(here::here("rmd/r_scripts_raw/preprocessing_2_chemistry.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_3_bap.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_4_habitat.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_5_user_perception.R"))
source(here::here("rmd/r_scripts_raw/preprocessing_6_tox.R"))
source(here::here("rmd/r_scripts_raw/appendices_and_data_package.R"))
```
\begin{center} 

Small Title



Brian T. Duffy 
Keleigh Reynolds  
Jeff J. Lojpersberger 
Meredith Streeter  






Stream Monitoring and Assessment Section  
New York State Department of Environmental Conservation  
Division of Water  
Bureau of Water Assessment and Management  
Albany, New York  
\end{center}

<!---CHUNK_PAGEBREAK--->

<!---BLOCK_TOC--->

<!---CHUNK_PAGEBREAK--->


# General
```{r child="child/section1_General.Rmd"}

```
\newpage

# Section I: Overview

```{r child="child/section1A_chemistry_stream_discharge.Rmd"}

```
\newpage

## Benthic Macroinvertebrate Community 
```{r child="child/section1B_BAP.Rmd"}

```
\newpage

## Stream Reach Physical Characteristics
```{r child="child/section1C_stream_reach_phys.Rmd"}

```
\newpage

## User Perception
```{r child="child/section1D_User_Perception.Rmd"}

```
\newpage


```{r child="child/section1E_tox.Rmd"}

if(params$tox){cat("# Sediment and Porewater Microtox® Analysis")}
```

\newpage
# Section II: Site Specific Data

```{r child="child/section_2_short.Rmd"}
#child="child/section_2_short.Rmd"
```

\newpage
# Conclusion



# Section III: Literature Cited

```{r appendices, echo=FALSE, warning=FALSE, message=FALSE}
block_pour_docx(file = here::here(paste("data",lit_cited_file,sep ="/")))
```


# Section IV: Appendices

```{r child="child/appendices.Rmd"}

```

