---
title: "SMAS_Violations"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "2/10/2021"
output: html_document
params:
    year.input: 2010
    sites_file_name: "sites_keuka.csv"
    user: kareynol
---

### Violation Analysis for Streams Data

This rmd will walk you through how to use the stayCALM package to analyze stream's data for violations of WQS, according to the CALM 2020. It utilizes the stayCALM package (Z.Smith, 2020) and data from the data modernization tables for stream/river data. (does this have a name?). Above you will see the parameters have year input and file name for the sites.

```{r}
#create the file path
file_path=file.path(here::here(),
                      "data")
sites_file_name=params$sites_file_name
year.input=params$year.input
user=params$user
```

Read in the SMAS files from the db, plus specify the subset of samples to run the script on. The subset file is an excel file that you specify the site ID's. Make sure the file you want to run this on is set in the "data" folder.

```{r}

#load the data needed for the subset of sites
sites<-read.csv(paste(file_path,params$sites_file_name,sep="/"),stringsAsFactors = FALSE)

```

Running the preprocessing script will limit all SBU data to just what you want, including chemistry and in-situ data.

```{r, message=FALSE,warning=FALSE}
#run the preprocessing 1 file that limits chemistry and insitu data to what we want
source(here::here("rmd","r_scripts_raw/functions.R"))
source(here::here("rmd","r_scripts_raw/preprocessing_1_raw.R"))

#this one does a lot so we can clean up what we don't need
rm(analyte,habitat.short,metrics.short,sbu.chem.statewide,sbu.insitu.statewide,tox.sed.short,tox.wat.short,userp.short)

```

Now you will need to run another processing script that will change column names to match, parameter names to match and join the chemistry and in-situ into one data frame.

```{r}
#first read in the pwl to get the segment id in both files
pwl<-sites.short %>% 
  select(SITE_HISTORY_ID,SITE_PWL_ID)

#merge with chem and insitu to get the pwl id into those files
chem.short<-merge(chem.short,pwl, by.x="CHS_EVENT_SMAS_HISTORY_ID",by.y="SITE_HISTORY_ID")

in.situ.short<-merge(in.situ.short,pwl, by.x="ISWC_EVENT_SMAS_HISTORY_ID",by.y="SITE_HISTORY_ID")

#read in the colnames change 
colnames_ref<-read.csv(here::here("data/col_names/stayCALM_colnames.csv"),stringsAsFactors = FALSE)

#function to change colnames for chemistry
colnames_smas_chem<-function(df){
  chem.good<-df
  col.from<-names(chem.good)
  col.vec.short<-colnames_ref %>% 
    subset(chem_db_col %in% col.from)
  
  names(chem.good)[match(col.vec.short[,"chem_db_col"],names(chem.good))]=col.vec.short[,"stayCALM_col"] #match the column names
  
  #subset the new names from what you just did and then remove the rest
  forstayCALM.colvec<-unique(col.vec.short$stayCALM_col)
  
  chem.good<-chem.good[,forstayCALM.colvec]
  
  #create empty data frame for the stayCALM package to merge with the final to have all of the columns you need
  
  #first create the list for all stay CALM colnames
  sc_all_cols<-unique(colnames_ref$stayCALM_col)
df1 <- data.frame(matrix(vector(),ncol=max(length(sc_all_cols))))#creates an empty data frame
colnames(df1) <-c(sc_all_cols) #renames the columns

chem.good<-merge(chem.good,df1,all.x=TRUE)
.GlobalEnv$chem.good<- chem.good #make available

}

colnames_smas_chem(chem.short)

```

```{r}

#function to change colnames for insitu
colnames_smas_insitu<-function(df){
  insitu.good<-df
  col.from<-names(insitu.good)
  col.vec.short<-colnames_ref %>% 
    subset(insitu_db_col %in% col.from)
  
  names(insitu.good)[match(col.vec.short[,"insitu_db_col"],names(insitu.good))]=col.vec.short[,"stayCALM_col"] #match the column names
  
  #subset the new names from what you just did and then remove the rest
  forstayCALM.colvec<-unique(col.vec.short$stayCALM_col)
  
  insitu.good<-insitu.good[,forstayCALM.colvec]
  
  #create empty data frame for the stayCALM package to merge with the final to have all of the columns you need
  
  #first create the list for all stay CALM colnames
  sc_all_cols<-unique(colnames_ref$stayCALM_col)
df1 <- data.frame(matrix(vector(),ncol=max(length(sc_all_cols))))#creates an empty data frame
colnames(df1) <-c(sc_all_cols) #renames the columns

insitu.good<-merge(insitu.good,df1,all.x=TRUE)
.GlobalEnv$insitu.good<- insitu.good #make available

}

colnames_smas_insitu(in.situ.short)
#change parameter names to match for the stayCALM package to run
```

```{r}
#bind the two into one df

all.chemistry<-rbind(chem.good,insitu.good)

all.chemistry$fraction<-tolower(all.chemistry$fraction)
all.chemistry$units<-tolower(all.chemistry$units)

#fix the DO fraction and PH
all.chemistry<-all.chemistry %>% 
  mutate(fraction=case_when(parameter=="DISSOLVED OXYGEN"& units=="mg/l"~"dissolved",
                            parameter=="PH" & units=="ph units"~"total",
                            TRUE~paste(fraction)))

#correct the parameter names for stayCALM

#read in the parameter correction file
param.names<-read.csv(paste(file.path,"/col_names/stayCALM_parameters.csv",sep = ""),stringsAsFactors = FALSE)

param.names.short<-param.names %>% 
  select(CHEM_PARAMETER_NAME,stayCALM_parameter,stayCALM_units,stayCALM_fraction)

all.chemistry<-merge(all.chemistry,param.names.short,by.x=c("parameter","fraction","units"),by.y=c("CHEM_PARAMETER_NAME","stayCALM_fraction","stayCALM_units"),all.x = TRUE)
  

#now clean up the columns by pasting the old parameter names to any that are blank (that means they aren't part of the stayCALM package)

all.chemistry<-all.chemistry %>% 
  mutate(stayCALM_parameter=case_when(stayCALM_parameter==""~paste(parameter),
                                      is.na(stayCALM_parameter)~paste(parameter),
                                      TRUE~paste(stayCALM_parameter)))

#make them all lowercase
all.chemistry$stayCALM_parameter<-tolower(all.chemistry$stayCALM_parameter)

#subset to keep the columns we need
all.chemistry<-all.chemistry %>% 
  select(!c(parameter)) %>% 
  rename(parameter=stayCALM_parameter)


#need to make new sample_ID columns since some are formated differently
all.chemistry$date<-as.Date(all.chemistry$date,"%m/%d/%Y")
all.chemistry$date_text<-format(all.chemistry$date,"%Y%m%d")

all.chemistry$sample_id<-paste(all.chemistry$site_id,all.chemistry$date_text,sep="_")
all.chemistry$date_text<-NULL

#write to file
write.csv(all.chemistry,here::here("outputs/dodge_prepped_good.csv"))

```


Now that the file is all set, we can run it through the violation steps from the stayCALM package.

```{r}
# Extract the package root with base R functions.
# This directory will provide relative paths between machines.
library(stayCALM)
root.dir <- gsub("(stayCALM)(.*$)", "\\1", getwd())

wqs.df <- stayCALM::nysdec_wqs
data("wipwl.df")

wqs_wipwl.df <- wipwl.df %>%
  # Subset columns
  select(seg_id, class, spatial_extent, water_type) %>% 
  # Ensure all rows are unique representations of the data.
  distinct() %>%
  # Join the DF with the WQS by the specified columns.
  left_join(wqs.df,
            by = c("class",
                   "spatial_extent",
                   "water_type"))

```

```{r}

chem_extract.df <- all.chemistry %>% 
  filter(parameter %in% c("hardness", "ph", "temperature")) %>% 
  tidyr::pivot_wider(
    id_cols = sample_id,
    names_from = "parameter",
    values_from = c("value", "units"),
    names_sep = "_",
    values_fn = list(value = mean,
                     units = unique,
                     na.rm = TRUE)
  ) %>% 
  right_join(all.chemistry, by = "sample_id")

#fix the units/results
wqs.short<-wqs_wipwl.df %>% 
  select(seg_id,parameter,fraction,units) %>% 
  rename(units_threshold=units)

chem_extract.df<-merge(chem_extract.df,wqs.short,by=c("seg_id","parameter","fraction"),all.x = TRUE)

chem_extract.df$value<-as.numeric(chem_extract.df$value)
#fix units that don't match

#take out any blanks
#chem_extract.df<-chem_extract.df %>% 
 # filter(value!="")

chem_extract.df$value<-as.numeric(chem_extract.df$value)


#correct them based on the units in the stds, and convert corrected value column to numeric
chem_extract.df$corrected_value<-ifelse(chem_extract.df$units=="mg/l" & chem_extract.df$units_threshold=="ug/l",
                                        chem_extract.df$value*1000,paste(chem_extract.df$value))
chem_extract.df$corrected_value<-ifelse(is.na(chem_extract.df$corrected_value),
                                        chem_extract.df$value,chem_extract.df$corrected_value)
chem_extract.df$corrected_value<-as.numeric(chem_extract.df$corrected_value)

#have to have it merge by units_threshold to get the match
chem_extract.df$value<-NULL
chem_extract.df$units<-NULL
chem_extract.df<-chem_extract.df %>% 
  rename(value=corrected_value,
         units=units_threshold)

chem.df <- merge(x = chem_extract.df, 
                 y = wqs_wipwl.df,
                 by = c("seg_id", "parameter",
                        "fraction", "units"))

chem.df <- thresh_determination(chem.df)

chem.df$date<-as.Date(chem.df$date,"%m/%d/%Y")
chem.df$year<-format(chem.df$date,"%Y")
chem.df$month<-format(chem.df$date,"%m")

chem.df$assessment_id <- group_id(.data = chem.df,
                                  .keep = c("seg_id",
                                            "parameter",
                                            "fraction"),
                                  .numeric = TRUE)

chem.df$within_period <- assessment_period(.date_vec = chem.df$date,
                                           .n_years_ago = 10)

prepped.df <- prep_values(.data = chem.df,
                          .block_col = "block",
                          .value_col = "value",
                          .statistic_col = "statistic",
                          .new_value_col = "result",
                          .min_n_col = "min_n")

selected.df <-
  subset(
    prepped.df,
    select = c(
      "assessment_id",
      "seg_id",
      "site_id",
      "water_type",
      "type",
      "use",
      "standard_type",
      "group",
      "block",
      "statistic",
      "parameter",
      "fraction",
      "units",
      "result",
      "date",
      "year",
      "within_period",
      "direction",
      "threshold",
      "summarize_rows",
      "summarize_rows_operator",
      "wqs_75p_threshold",
      "data_provider"
    )
  )

selected.df$attaining_wqs <- attaining(selected.df$result,
                                       selected.df$direction,
                                       selected.df$threshold)

selected.df$attaining_75 <- attaining(selected.df$result,
                                      selected.df$direction,
                                      selected.df$wqs_75p_threshold)

temp4<-selected.df%>%
  group_by(site_id, parameter, fraction, date)%>%
  summarize(n=n(),
            combined=sum(attaining_wqs),
            WQS_attain_combined= ifelse(combined==n, yes=TRUE, no=FALSE),
            num_standards=(n-combined))

temp5<-selected.df %>% 
  group_by(seg_id,parameter,fraction,units,date) %>% 
  summarize(n=n(),
            combined=sum(attaining_wqs),
            WQS_attain_combined= ifelse(combined==n, yes=TRUE, no=FALSE),
            num_standards=(n-combined))

temp5$year<-format(temp5$date,"%Y")
temp5<-temp5 %>% 
  group_by(seg_id,year,parameter) %>% 
  mutate(exceed=case_when(
    WQS_attain_combined=="FALSE"~1,
    TRUE~0
  )) %>% 
  summarise(Exceedances=sum(exceed)) %>%
  filter(Exceedances!=0) %>% 
  rename(PWL_segment=seg_id,
         Year=year,
         Parameter=parameter)

#write.csv(temp5,"outputs/fl_exceedances.csv",row.names = FALSE)
#From here you should be able to left join pwls or raw data back on or filter to do summaries to create tables etc. 

#clean up
rm(list=ls()[! ls() %in% c("temp4","selected.df","wqs_wipwl.df","temp5")])


```








