---
title: "Section II: Site Specific Data"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "`r Sys.Date()`"
output:
  officedown::rdocx_document:
    reference_docx: template.docx
params:
    tox: FALSE
    study_name: "Birch Creek at Belleayre Mountain Ski Area"
    year_input: 2019
    intro_file_name: "birch_intro.csv"
    sites_file_name: "birch_sites.csv"
    grouping_for_chem: site
    grouping_for_bap: site
    map_zoom: 12
    user: kareynol
    limit_to_nuts: TRUE
    data_package: TRUE
---
Section II provides a summary of results from each sampling location. Descriptive tables include applicable established water quality standards (6 NYCRR Part 703), as well as narrative standards. Nutrients are regulated by a narrative water quality standard stating: “None in amounts that result in growths of algae, weeds, and slimes that will impair the waters for their best usages” (6 NYCRR 703.2).

Data tables include a summary of general chemistry, in situ chemistry results, BAP scores and instantaneous discharge (where available). Water chemistry results are summarized by number of records reported after meeting quality assurance standards, and a statistical summary that includes mean, median, standard deviation (SD), minimum, and maximum concentrations. Violations of water quality standards at each site are also included. Complete, quality assured raw chemistry data results accompanied by all applicable standards are available in Attachment I (excel file). BAP scores are provided and include date of the sample,mean BAP score, standard deviation (SD), standard error (SE) and number of records. Instantaneous stream discharge (cubic feet/second) is reported for dates when conditions allowed safe, wadeable access to streams (RAS QAPP (17-19); SOP #210-21).

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

study_name=params$study_name
tox=params$tox
intro_file_name=params$intro_file_name
sites_file_name=params$sites_file_name
year.input=params$year_input
#updated_sites_file_name=params$updated_sites_file_name
grouping_for_bap=params$grouping_for_bap
grouping_for_chem=params$grouping_for_chem
map_zoom=params$map_zoom
user=params$user
limit_to_nuts=params$limit_to_nuts
data_package=params$data_package

library(stringr)
library(dplyr)

source(here::here("rmd/r_scripts_raw/preprocessing_7_sect_2.R"))

```


```{r include=FALSE}
#FUNCTIONS

table.f<-function(df,x,y){
 
  tl<-flextable::flextable(df) %>% 
    flextable::font(i = NULL, j = NULL, fontname="Arial", part = "all") %>% 
    flextable::theme_zebra() %>% 
    flextable::autofit()
tl<- flextable::align(tl, i = NULL, j =(x:y) , align = "center", part = "all")
tl<-flextable::fit_to_width(tl,max_width = 7.5)
tl<-flextable::fontsize(tl, i = NULL, j = NULL, size = 9, part = "body")
return(tl)
}

#get pwl lines for map
#mapl<-read.csv(here::here("data","map_lines_use.csv"),stringsAsFactors = FALSE)

#map function
map.me<-function(df1,df2){
  df1$SITE_LONGITUDE<-as.numeric(df1$SITE_LONGITUDE)
  df1$SITE_LATITUDE<-as.numeric(df1$SITE_LATITUDE)
  df2$SITE_LATITUDE<-as.numeric(df2$SITE_LATITUDE)
  df2$SITE_LONGITUDE<-as.numeric(df2$SITE_LONGITUDE)
  #bounding box
library(ggmap)
dodge_map<-read.csv(here::here("data/dodge_map.csv"),stringsAsFactors = FALSE)
  
#nybox<-make_bbox(df1,lon=SITE_LONGITUDE,lat=SITE_LATITUDE)
nybox<-make_bbox(dodge_map,lon=SITE_LONGITUDE,lat=SITE_LATITUDE)


ny.map<-qmap(nybox, source = "osm",color="bw", zoom=params$map_zoom)+
  #geom_path(data=subset(mapl,type=="trib"),aes(x = long, y = lat,group=group),color="steelblue1",alpha=0.5,,na.rm=TRUE)+
  #geom_path(data=subset(mapl,type=="main"),aes(x = long, y = lat,group=group),color="slateblue3",size=0.9,,na.rm=TRUE)+
geom_point(data=df1,aes(x=SITE_LONGITUDE,y=SITE_LATITUDE),
                  color="yellow",size=4)+
  geom_point(data=df2,aes(x=SITE_LONGITUDE,y=SITE_LATITUDE),color="red",size=4)
  
print(ny.map)
  
}

#table.f<-function(df, center.cols){
 
 # tl<-flextable::flextable(df) %>% 
  #  flextable::font(i = NULL, j = NULL, fontname="Arial", part = "all") %>% 
   # flextable::theme_zebra() %>% 
    #flextable::autofit()
#tl<- flextable::align(tl, i = NULL, j = center.cols, align = "center", part = "all")
#return(tl)
#}
#table.f(mer_short.df, c("min", "max")) %>% 
 # flextable::align(i = NULL, j = "SITE_ID", align = "center", part = "all")

#x.vec
```

```{r sites_chem, fig.cap="Map of site locations. Specific site is red, sites in the rest of the study are mapped in yellow.", warning=FALSE, echo=FALSE,message=FALSE, results='asis',fig.align="center"}

sites<-sites %>% 
  arrange(order)
sites$order<-as.numeric(sites$order)
#sites$SITE_HISTORY_ID<-fct_reorder(sites$SITE_HISTORY_ID,sites$order)

sites.l<-unique(sites$SITE_HISTORY_ID)

 for (i in seq_along(sites.l)) { 
    #print(i)
  site.loc.small<-sites[sites$SITE_HISTORY_ID %in% sites.l[i],]
   
  stds_small<-unique(site.loc.small$SITE_WATER_QLTY_STANDARD)
  stds_small<-toupper(stds_small)
  site<-unique(site.loc.small$SITE_HISTORY_ID)
  
  pwl_small<-unique(site.loc.small$SITE_PWL_ID)
  
   
   cat("  \n\n###  ",paste(sites.l[i]), "| Waterbody Class:",stds_small,"| PWL_ID:",pwl_small)


   map.me(sites,site.loc.small)
   
  temp.stds<-wqs_table %>% 
    filter(`Waterbody Class`==stds_small) %>% 
    distinct()
  
  list.params<-temp6[temp6$site_id %in% sites.l[i],]
  
  list.params.l<-unique(list.params$parameter)
  
  temp.stds<-temp.stds %>% 
    subset(Parameter %in% list.params.l)
  
  tab<-table.f(temp.stds,2,max(ncol(temp.stds)))
  label=paste("Applicable Standards:",sites.l[i])
  tab<-tab %>% 
    flextable::set_caption(label)
  flextable::docx_value(tab)
  flextable::fit_to_width(tab,max_width = 6)
  
  rm(temp)
   cat("  \n")
   cat("<br><br>")
  
  temp <-chem_sum.df[chem_sum.df$SITE_ID %in% sites.l[i], ]
  temp$SITE_ID<-NULL
  
  tab1<-table.f(temp, 2,max(ncol(temp)))
  label=paste("Chemistry Measurements:",sites.l[i])
  tab1<-flextable::set_caption(tab1,label)
   flextable::docx_value(tab1)
   flextable::fit_to_width(tab1,max_width = 6)
   rm(temp)
   cat("  \n")
   cat("<br><br>")
   
  temp <-insitu_sum.df[insitu_sum.df$SITE_ID %in% sites.l[i], ]
  temp$SITE_ID<-NULL
   if (nrow(temp) > 0){tab2<-table.f(temp, 2,4)
   label=paste("In-Situ Measurements:",sites.l[i])
   tab2<-flextable::set_caption(tab2,label)
   flextable::docx_value(tab2)}
   rm(temp)
   cat(rep("\n", 10))
   cat("<br><br>")
   
   temp<-all_exceedances.df[all_exceedances.df$Site %in% sites.l[i],]
   temp$Site<-NULL
   temp<-temp %>% 
     distinct() #take out the repeats
   
 
   if (nrow(temp) > 0){   
     tab3<-table.f(temp,2,4)
   label=paste("Water Quality Standard Violations:",sites.l[i])
   tab3<-flextable::set_caption(tab3,label)
   flextable::docx_value(tab3)}
   else{
       cat("  \n\n *Water Quality Standard Violations*")
     cat("  \n\n There were no water quality standard violations at this site during the sampling period.")
   }
   rm(temp)
     cat(rep("\n"))
   cat("<br><br>")
   
  #temp <-nnc_sum.df[nnc_sum.df$SITE_ID %in% sites.l[i], ]
  #temp$SITE_ID<-NULL
   #if (nrow(temp) > 0){tab4<-table.f(temp, 2,4)
   #label=paste("Numeric Nutrient Criteria:",sites.l[i])
   #tab4<-flextable::set_caption(tab4,label)
   #flextable::docx_value(tab4)}
   #rm(temp)
   #cat("  \n")
   #cat("<br><br>")
  
  temp<-bap.df[bap.df$MSSIH_EVENT_SMAS_HISTORY_ID %in% sites.l[i], ]
  temp$MSSIH_EVENT_SMAS_HISTORY_ID<-NULL
  if (nrow(temp) > 0){
  tab6<-table.f(temp,1,2)
  label=paste("Biological Assessment Score (BAP) Summary: ",sites.l[i])
  tab6<-flextable::set_caption(tab6,label)
  flextable::docx_value(tab6)}
  rm(temp)
  cat("  \n")
  cat("<br><br>")
  
  temp<-flow[flow$SEIH_EVENT_SMAS_HISTORY_ID%in% sites.l[i], ]
  if (nrow(temp) > 0) {
    library(ggplot2)
    tab5<-ggplot(temp,aes(SEIH_EVENT_SMAS_SAMPLE_DATE,SEIH_TOTAL_DISCH)) +
      geom_point()+
        ylab("cfs")+
      xlab("Discharge measured in cubic feet per second (cfs).")+
      scale_x_date(date_labels = "%b %Y")
    print(tab5)
    rm(temp)
  }


  cat("  \n")
  
 }

    # create plot for each PWL in df 
    
```
