---
title: "section1_General"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "`r Sys.Date()`"
output: 
word_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
intro<-read.csv(here::here("data",intro_file_name),stringsAsFactors = FALSE)

```

`r paste(intro$intro)`

The Steam Monitoring and Assessment Section (SMAS) conducted targeted stream monitoring that included:

`r if(bap){paste("*  Benthic Macroinvertebrate Community Analysis")}`
-   Water Quality Measurements
`r if(habitat){paste("*  Stream Reach Physical Habitat Characteristics")}`
-   Observer Ranking of Recreational Ability
`r if(tox){paste("* Sediment and Porewater Microtox Analysis")}`

This data report includes two sections: I) an overview of the sampling events described above, `r if(grouping_for_chem=="PWL"){paste("with results aggregated by WI/PWL segment,")}` and II) a site-specific data summary to present all major findings for each site. Additional sections (III, IV) include literature cited and appendices covering all references and additional source material.

The `r params$study_name` site descriptions (Table \@ref(tab:sites-table)) and locations (Figure \@ref(fig:site-map)), and sampling dates (Table \@ref(tab:sites-dates)) are included below.

```{r tab.id="sites-table",  echo=FALSE, message=FALSE, warning=FALSE, }

library(dplyr)
library(flextable)
# tl<-flextable(table1) %>% font(i = NULL, j = NULL, fontname="Arial", part = "all") %>% theme_zebra() %>% autofit()
# tl<-align(tl, i = NULL, j =(2:5) , align = "center", part = "all")%>%
#   fontsize(size=8, part = "all")%>%
#   fontsize(j=6, size=7)%>%
#   width(j=c(1), width=1)%>%
#   width(j=c(5), width=0.8)%>%
#   width(j=c(4,7,8), width=0.6)%>%
#   width(j=c(2), width=0.7)%>%
#   width(j=c(3), width=0.6)%>%
#   width(j=6, width=2.5)
tl<-table.f(table1,2,max(ncol(table1)))
tl<-flextable::set_caption(tl,caption="Sampling locations.",style="Table Caption",autonum = run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
# tl<-fit_to_width(tl,7.5)
tl
```

```{r site-map, echo=FALSE, fig.cap="Map of sampling locations. Site names reference the Location ID and River Mile.", message=FALSE, warning=FALSE}

knitr::include_graphics(here::here(paste("data/map/",params$map_file,sep = "")))
  
```

```{r tab.id="sites-dates",  echo=FALSE, message=FALSE, warning=FALSE }

tl<-table.f(dates_all,2,max(ncol(dates_all)))
tl<-set_caption(tl,caption = "Sampling dates and overall parameters for the study period included in this report.",style="Table Caption",autonum = run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
tl
```
