---
title: "Section 2: Site Specific Data"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "`r Sys.Date()`"
output: 
word_document: default

---
Section II provides a tabular summary of all accepted results from each sampling location. Descriptive tables for each site include applicable established WQS (6 NYCRR Part 703), a summary of general chemistry and in-situ results and WQS excursion information. `r if(bap){paste("Tables also inclde BAP scores.")}` Water chemistry results are summarized by analyte concentration after meeting QA/QC standards. WQS excursion information identifies excursions of the applicable WQS.`r if(bap){paste(" BAP score information includes mean BAP score, standard deviation, standard error, and number of replicates.")}`

```{r include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#library(stringr)
#library(dplyr)

#source(here::here("rmd/r_scripts_raw/preprocessing_7_sect_2.R"))

#disable the scientific notation 
#options(scipen=99)



```

```{r tab.id="sites_chem",results = 'asis',warning=FALSE, echo=FALSE,message=FALSE}

sites<-sites.short %>% 
  arrange(order)
sites$order<-as.numeric(sites$order)
#sites$SITE_HISTORY_ID<-fct_reorder(sites$SITE_HISTORY_ID,sites$order)

sites.l<-unique(sites$SITE_HISTORY_ID)
#add the sites for the FL
#sites.add<-unique(ext$CHS_EVENT_SMAS_HISTORY_ID)
#sites.l<-merge(sites.add,sites.l)

 for (i in seq_along(sites.l)) { 
    #print(i)
  pwl_sc<-chem_export %>%
    select(`PWL segment`,Class,Site) %>% 
    distinct()#use the stayCALM seg ID to limit to class, might need to update, this is only looking at those that went through stayCALM
  
  site.loc.small<-pwl_sc[pwl_sc$Site %in% sites.l[i],]
   
  stds_small<-unique(site.loc.small$Class)
  stds_small<-toupper(stds_small)
  site<-unique(site.loc.small$Site)
  
  pwl_small<-unique(site.loc.small$`PWL segment`)
  site.loc.small<-sites[sites$SITE_HISTORY_ID %in% sites.l[i],]
   
   
   cat("  \n\n###  ",paste(sites.l[i]), "| Waterbody Class:",stds_small,"| WI/PWL ID:",pwl_small)
   cat("  \n")
   cat("<br><br>")


   #map.me(sites,site.loc.small)
   
  temp.stds<-wqs_table %>% 
    filter(Class==stds_small) %>% 
    distinct()
  
  list.params<-raw_df_export[raw_df_export$site_id %in% sites.l[i],]
  list.params$parameter<-stringr::str_to_title(list.params$parameter)
  
  list.params.l<-unique(list.params$parameter)
  
  temp.stds<-temp.stds %>% 
    subset(Parameter %in% list.params.l)
  temp.stds<-temp.stds %>% 
    mutate(Parameter=case_when(Parameter=="Ph"~"pH",
                               Parameter=="Dissolved_oxygen"~"Dissolved Oxygen",
                               Parameter=="Nitrate_nitrite"~"Nitrate-nitrite",
                               TRUE~paste(Parameter)))
  
  label=paste("Applicable Standards:",sites.l[i])
  tab.cap=paste(label)
  tab<-table.f(temp.stds,2,max(ncol(temp.stds)))
  #label=paste("Applicable Standards:",sites.l[i])
  tab<-flextable::set_caption(tab,tab.cap,style="Table Caption",autonum = run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
 # tab<-tab %>% 
    #flextable::width(j=NULL,3)
  flextable::fit_to_width(tab,max_width = 3) 
  flextable::autofit(tab)
  flextable::flextable_to_rmd(tab)
  
  rm(temp)
  rm(tab.label)
   cat("  \n")
   cat("<br><br>")
  
  temp <-chemistry_section2[chemistry_section2$Site %in% sites.l[i], ]
  temp$Site<-NULL
  temp$Parameter<-stringr::str_to_title(temp$Parameter)

  
  if(max(temp$`Record Count`)<= 1){
    temp<-temp %>% 
      select(-c(Median,Max,Min)) %>% 
      rename(Result=Mean)
  }
  
 if (nrow(temp) > 0){ 
   label=paste("Chemistry Measurements:",sites.l[i])
   tab.cap=paste(label)
   tab1<-table.f(temp, 2,max(ncol(temp)))
  #label=paste("Chemistry Measurements:",sites.l[i])
  tab1<-flextable::set_caption(tab1,tab.cap,style="Table Caption",autonum = run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
  flextable::fit_to_width(tab1,max_width = 3) 
  flextable::flextable_to_rmd(tab1)
   rm(temp)
   cat("  \n")
   cat("<br><br>")
 }
   
   temp <-field[field$Site %in% sites.l[i], ]
   temp$Site<-NULL
   
     if(max(temp$`Record Count`)<= 1){
    temp<-temp %>% 
      select(-c(Median,Max,Min)) %>% 
      rename(Result=Mean)
     }
   
  temp$Parameter<-stringr::str_to_title(temp$Parameter)
   temp<-temp %>% 
    mutate(Parameter=case_when(Parameter=="Ph"~"pH",
                               TRUE~paste(Parameter)))
  
   if (nrow(temp) > 0){ tab1<-table.f(temp, 2,max(ncol(temp)))
  label=paste("In-Situ Measurements:",sites.l[i])
  tab.cap=paste(label)
  tab1<-flextable::set_caption(tab1,tab.cap,style="Table Caption",autonum = run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
  flextable::fit_to_width(tab1,max_width = 3) 
   flextable::flextable_to_rmd(tab1)}

   rm(temp)
   cat("  \n")
   cat("<br><br>")
   
   temp<-viol_small[viol_small$site_id %in% sites.l[i],]
   temp<-temp %>% 
     select(!c(site_id,seg_id,statistic,sample_count,sample_count,use))
   temp<-temp %>% 
     distinct() #take out the repeats
 
     temp<-temp %>% 
       rename(Date=date,
              Parameter=parameter,
              Result=result,
              Fraction=fraction,
              Units=units,
              Threshold=threshold,
              Excursion=attaining_wqs)
      temp<-temp %>% 
        mutate(Excursion=case_when(Excursion=="no"~"Excursion",
                                   TRUE~"No Excursion"))

     temp<-temp %>% 
       filter(Excursion=="Excursion") %>% 
       select(!Excursion)#filter to just the violations and then remove that column
     
     temp$Parameter<-stringr::str_to_title(temp$Parameter)
     temp<-temp %>% 
    mutate(Parameter=case_when(Parameter=="Ph"~"pH",
                               Parameter=="Dissolved_oxygen"~"Dissolved oxygen",
                               TRUE~paste(Parameter)),
           Units=case_when(Units=="ph units"~"pH units",
                           TRUE~paste(Units)))
  if (nrow(temp) > 0){ 
     tab3<-table.f(temp,2,4)
   label=paste("Water Quality Standard Excursions:",sites.l[i])
   tab.cap=paste(label)
   tab3<-flextable::set_caption(tab3,tab.cap,style="Table Caption",autonum = run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
   flextable::fit_to_width(tab3,max_width = 3) 
   flextable::flextable_to_rmd(tab3)}
   else{
       cat("  \n\n *Water Quality Standard Excursions*")
     cat("  \n\n There were no water quality standard excursions at this site during the sampling period.")
   }
   rm(temp)
     cat(rep("\n"))
   cat("<br><br>")
   
  #temp <-nnc_sum.df[nnc_sum.df$SITE_ID %in% sites.l[i], ]
  #temp$SITE_ID<-NULL
   #if (nrow(temp) > 0){tab4<-table.f(temp, 2,4)
   #label=paste("Numeric Nutrient Criteria:",sites.l[i])
   #tab4<-flextable::set_caption(tab4,label)
   #flextable::docx_value(tab4)}
   #rm(temp)
   #cat("  \n")
   #cat("<br><br>")
  if(bap){
  temp<-bap.df[bap.df$MSSIH_EVENT_SMAS_HISTORY_ID %in% sites.l[i], ]
  temp$MSSIH_EVENT_SMAS_HISTORY_ID<-NULL
  if (nrow(temp) > 0){
  tab6<-table.f(temp,1,2)
  label=paste("Biological Assessment Score (BAP) Summary: ",sites.l[i])
  tab.cap=paste(label)
  tab6<-flextable::set_caption(tab6,tab.cap,style="Table Caption",autonum = run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
  flextable::flextable_to_rmd(tab6)}
  rm(temp)
  cat("  \n")
  cat("<br><br>")
  }
  
  temp<-flow[flow$SEIH_EVENT_SMAS_HISTORY_ID%in% sites.l[i], ]
  if (nrow(temp) > 0) {
    library(ggplot2)
    tab5<-ggplot(temp,aes(SEIH_EVENT_SMAS_SAMPLE_DATE,SEIH_TOTAL_DISCH)) +
      geom_point()+
        ylab("cfs")+
      xlab("Discharge measured in cubic feet per second (cfs).")+
      scale_x_date(date_labels = "%b %Y")
    print(tab5)
    rm(temp)
  }


  cat("  \n")
  
 }

    # create plot for each PWL in df 
    
```
