---
title: "section2_sitespecificData"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "4/24/2020"
output:
  word_document: default
params:
    tox: FALSE
    study_name: "Halfway Creek Monitoring"
    year_input: 2010
    intro_file_name: "halfway_intro.csv"
    sites_file_name: "halfway_sites.csv"
    updated_sites_file_name: "halfway_sites_to_assign_order.csv"
    map_zoom: 12     
---
Section II provides a summary of results from each sampling location. Data provided includes waterbody class and WI/PWL number along with a summary of general chemistry, in situ chemistry results, BAP scores and instantaneous discharge. Water chemistry results are summarized by number of records reported after quality assurance (Appendix V), exceedances of water quality standards and a statistical summary that includes mean, median, minimum, and maximum concentrations. Specific exceedances of water quality standards are also specified. Complete, quality assured raw chemistry data results accompanied by all applicable standards are available in electronic form (attached). BAP scores are provided and include a statistical summary of results for each site that includes mean, impairment threshold, minimum, maximum, standard deviation and standard error. Instantaneous stream discharge (cubic feet/second) is reported for dates when conditions allowed safe, wadeable access to streams (RAS QAPP (17-19); SOP #210-19).

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(stringr)
library(dplyr)

study_name=params$study_name
tox=params$tox
intro_file_name=params$intro_file_name
sites_file_name=params$sites_file_name
year.input=params$year_input
updated_sites_file_name=params$updated_sites_file_name
year_input=params$year_input
map_zoom=params$map_zoom


source(here::here("rmd/r_scripts_raw/preprocessing_7_sect_2.R"))

#disable the scientific notation 
options(scipen=9999)

```


```{r include=FALSE}
#FUNCTIONS

table.f<-function(df,x,y){
 
  tl<-flextable::flextable(df) %>% 
    flextable::font(i = NULL, j = NULL, fontname="Arial", part = "all") %>% 
    flextable::theme_zebra() %>% 
    flextable::autofit()
tl<- flextable::align(tl, i = NULL, j =(x:y) , align = "center", part = "all")
tl<-flextable::fit_to_width(tl,max_width = 7.5)
tl<-flextable::fontsize(tl, i = NULL, j = NULL, size = 9, part = "body")
return(tl)
}

#get pwl lines for map
#mapl<-read.csv(here::here("data","map_lines_use.csv"),stringsAsFactors = FALSE)

#map function
map.me<-function(df1,df2){
  #bounding box
library(ggmap)
nybox<-make_bbox(df1,lon=SITE_LONGITUDE,lat=SITE_LATITUDE)
 
ny.map<-qmap(nybox, source = "osm",color="bw",zoom=map_zoom)+
  #geom_path(data=subset(mapl,type=="trib"),aes(x = long, y = lat,group=group),color="steelblue1",alpha=0.5,,na.rm=TRUE)+
  #geom_path(data=subset(mapl,type=="main"),aes(x = long, y = lat,group=group),color="slateblue3",size=0.9,,na.rm=TRUE)+
geom_point(data=df1,aes(x=SITE_LONGITUDE,y=SITE_LATITUDE),
                  color="yellow",size=4)+
  geom_point(data=df2,aes(x=SITE_LONGITUDE,y=SITE_LATITUDE),color="red",size=4)
  
print(ny.map)
  
}

#table.f<-function(df, center.cols){
 
 # tl<-flextable::flextable(df) %>% 
  #  flextable::font(i = NULL, j = NULL, fontname="Arial", part = "all") %>% 
   # flextable::theme_zebra() %>% 
    #flextable::autofit()
#tl<- flextable::align(tl, i = NULL, j = center.cols, align = "center", part = "all")
#return(tl)
#}
#table.f(mer_short.df, c("min", "max")) %>% 
 # flextable::align(i = NULL, j = "SITE_ID", align = "center", part = "all")

#x.vec
```

```{r,warning=FALSE, echo=FALSE,message=FALSE, results='asis',fig.align="center"}


sites<-sites %>% 
  arrange(order)
sites$order<-as.numeric(sites$order)
sites$SITE_HISTORY_ID<-fct_reorder(sites$SITE_HISTORY_ID,sites$order)

sites.l<-unique(sites$SITE_HISTORY_ID)

 for (i in seq_along(sites.l)) { 
   # print(i)
  site.loc.small<-sites[sites$SITE_HISTORY_ID %in% sites.l[i],]
   
  stds_small<-unique(site.loc.small$SITE_WATER_QLTY_STANDARD)
  stds_small<-toupper(stds_small)
  site<-unique(site.loc.small$SITE_HISTORY_ID)
  
  pwl_small<-unique(site.loc.small$SITE_PWL_ID)
  
   
   cat("  \n\n###  ",paste(sites.l[i]), "| Waterbody Class:",stds_small,"| PWL_ID:",pwl_small)


   map.me(sites,site.loc.small)
   
  temp.stds<-wqs_table %>% 
    filter(`Waterbody Class`==stds_small) %>% 
    distinct()
  
  list.params<-temp6[temp6$site_id %in% sites.l[i],]
  
  list.params.l<-unique(list.params$parameter)
  
  temp.stds<-temp.stds %>% 
    subset(Parameter %in% list.params.l)
  
  tab<-table.f(temp.stds,2,max(ncol(temp.stds)))
  label=paste("Applicable Standards:",sites.l[i])
  tab<-flextable::set_caption(tab,label)
  flextable::docx_value(tab)
  flextable::fit_to_width(tab,max_width = 6)
  rm(temp)
   cat("  \n")
   cat("<br><br>")
  
  temp <-chem_sum.df[chem_sum.df$SITE_ID %in% sites.l[i], ]
  temp$SITE_ID<-NULL
  
  tab1<-table.f(temp, 2,max(ncol(temp)))
  label=paste("Chemistry Measurements:",sites.l[i])
  tab1<-flextable::set_caption(tab1,label)
   flextable::docx_value(tab1)
   flextable::fit_to_width(tab1,max_width = 6)
   rm(temp)
   cat("  \n")
   cat("<br><br>")
   
  temp <-insitu_sum.df[insitu_sum.df$SITE_ID %in% sites.l[i], ]
  temp$SITE_ID<-NULL
   if (nrow(temp) > 0){tab2<-table.f(temp, 2,4)
   label=paste("In-Situ Measurements:",sites.l[i])
   tab2<-flextable::set_caption(tab2,label)
   flextable::docx_value(tab2)}
   rm(temp)
   cat(rep("\n", 10))
   cat("<br><br>")
   
   temp<-all_exceedances.df[all_exceedances.df$Site %in% sites.l[i],]
   temp$Site<-NULL
   temp<-temp %>% 
     distinct() #take out the repeats
   
 
   if (nrow(temp) > 0){   
     tab3<-table.f(temp,2,4)
   label=paste("Water Quality Standard Violations:",sites.l[i])
   tab3<-flextable::set_caption(tab3,label)
   flextable::docx_value(tab3)}
   else{
       cat("  \n\n *Water Quality Standard Violations*")
     cat("  \n\n There were no water quality standard violations at this site during the sampling period.")
   }
   rm(temp)
     cat(rep("\n"))
   cat("<br><br>")
   
  #temp <-nnc_sum.df[nnc_sum.df$SITE_ID %in% sites.l[i], ]
  #temp$SITE_ID<-NULL
   #if (nrow(temp) > 0){tab4<-table.f(temp, 2,4)
   #label=paste("Numeric Nutrient Criteria:",sites.l[i])
   #tab4<-flextable::set_caption(tab4,label)
   #flextable::docx_value(tab4)}
   #rm(temp)
   #cat("  \n")
   #cat("<br><br>")
  
  temp<-bap.df[bap.df$MSSIH_EVENT_SMAS_HISTORY_ID %in% sites.l[i], ]
  temp$MSSIH_EVENT_SMAS_HISTORY_ID<-NULL
  if (nrow(temp) > 0){
  tab6<-table.f(temp,1,2)
  label=paste("Biological Assessment Score (BAP) Summary: ",sites.l[i])
  tab6<-flextable::set_caption(tab6,label)
  flextable::docx_value(tab6)}
  rm(temp)
  cat("  \n")
  cat("<br><br>")
  
  temp<-flow[flow$SEIH_EVENT_SMAS_HISTORY_ID%in% sites.l[i], ]
  if (nrow(temp) > 0) {
    library(ggplot2)
    tab5<-ggplot(temp,aes(SEIH_EVENT_SMAS_SAMPLE_DATE,SEIH_TOTAL_DISCH)) +
      geom_point()+
        ylab("cfs")+
      xlab("Discharge measured in cubic feet per second (cfs).")+
      scale_x_date(date_labels = "%b %Y")
    print(tab5)
    rm(temp)
  }


  cat("  \n")
  
 }

    # create plot for each PWL in df 
    
```
