---
title: "Section 1 a) chemistry and stream discharge"
author: 'NYSDEC SMAS : Keleigh Reynolds'
date: "4/10/2020"
output: 
word_document: default
---
### Water Chemistry Collection

```{r echo=FALSE, message=FALSE, warning=FALSE}
#get segments and other text for below
show_text_pwl<-unique(sites$SITE_PWL_ID)

temp7<-temp6
temp7<-temp7 %>% 
  mutate(parameter=case_when(parameter=="ph"~"pH",
                             parameter=="dissolved_oxygen"~"dissolved oxygen",
                             TRUE~parameter))
show_text_standards<-unique(temp7$parameter) 

show_text_ex<-temp5 %>% 
  select(Parameter,units) %>% 
  distinct() %>% 
  mutate(combo=paste(Parameter,units,sep = ","))

```

DEC establishes water quality standards (WQS) and guidance values for many specific substances. Waters are classified for their best uses and WQS are set to protect those uses (6 NYCRR Part 703). The data presented below does not meet the minimum data requirements for a confirmed best use assessment^[Best use assessment confirmation is based on 1) whether data are core or supplemental indicators, 2) how many years of data are available, and 3) how many samples were collected. (CALM, 2021)] (CALM, 2021). For the best use assessment, please see [DEC Info Locator](https://gisservices.dec.ny.gov/gis/dil/) and factsheets^[ Compilation of the state’s Integrated Report and updates to WI/PWL ID factsheets occur during even (2022, 2024) years. Best use assessments and factsheets may not immediately reflect data generated in this report.] for individual WI/PWL ID segments (WI/PWL ID `r paste(unique(show_text_pwl),sep=",")`). 

Ambient water chemistry sampling included in-situ and lab measured water quality analytes (Table \@ref(tab:Analytes)).  A total of `r length(unique(chem.short$CHEM_PARAMETER_NAME))`   lab-measured and `r length(unique(in.situ.short$CHEM_PARAMETER_NAME))` in-situ water quality parameters were collected. Samples were collected by SMAS using the direct grab method (SOP #210-21, section 11.6). Water samples were sent for processing using a contract lab with NYS Environmental Laboratory Approval Program (ELAP) certification. 

Following sample collection, all data processing followed quality assurance/quality control (QA/QC) protocols (SOP #102-20, and #110-21). Only data meeting the highest data quality standard were reported and used in this report. For water chemistry, an evaluation of the precision, accuracy, and completeness of processed water chemistry samples after lab analyses was performed following the methods detailed in SOP #102. Appendix I includes a compilation of all rejected data flagged by the process. Analytes that fell below the minimum detection limit (MDL) were replaced with 1/2 the MDL (Helsel, 1990). Where applicable, raw chemistry results were analyzed for excursions from state WQS and summarized using R programing software (R Core Team, 2017). All accepted raw chemistry results (in-situ and lab reported) with all applicable standards and excursion determinations accompany this report as Attachment I (excel file).

```{r, echo=FALSE,warning=FALSE, message=FALSE}
if(limit_to_nuts){
  chem.trans$CHEM_PARAMETER_NAME<-stringr::str_to_title(chem.trans$CHEM_PARAMETER_NAME)
    chem.trans<-chem.trans %>% 
      filter(CHEM_PARAMETER_NAME=="Nitrogen, Ammonia (As N)"|
             CHEM_PARAMETER_NAME=="Nitrogen, Kjeldahl, Total"|
             CHEM_PARAMETER_NAME=="Nitrogen, Nitrate-Nitrite"|
             CHEM_PARAMETER_NAME=="Nitrogen, Nitrate (As N)"|
             CHEM_PARAMETER_NAME=="Nitrogen, Nitrite"|
             CHEM_PARAMETER_NAME=="Nitrogen, Total"|
             CHEM_PARAMETER_NAME=="Phosphorus, Total (As P)"|
               CHEM_PARAMETER_NAME=="Phosphorus, Dissolved Orthophosphate (As P)")
   
      in.situ.short$CHEM_PARAMETER_NAME<-stringr::str_to_title(in.situ.short$CHEM_PARAMETER_NAME)
      in.situ.short<-in.situ.short %>% 
      filter(CHEM_PARAMETER_NAME=="Dissolved Oxygen"|
               CHEM_PARAMETER_NAME=="Temperature"|
               CHEM_PARAMETER_NAME=="Ph"|
               CHEM_PARAMETER_NAME=="Specific Conductance")
    }
```

A total of `r n_distinct(chem.short$CHEM_PARAMETER_NAME)` lab-measured, and `r n_distinct(in.situ.short$CHEM_PARAMETER_NAME)` in-situ water quality analytes were analyzed in this study. Out of the `r nrow(chem.short)` lab-measured records and `r nrow(in.situ.short)` in-situ water quality records, there were `r nrow(temp5)` excursions from established water quality standards (6 NYCRR Part 703). `r if(nrow(temp5 >1)){paste("There were excursions in")}`
`r if(nrow(temp5 >1)){paste(unique(show_text_ex$combo),sep="; ")}` 
  `r if(nrow(temp5 >1)){paste(".")}`

`r if(grouping_for_chem=="PWL"){paste("Plots illustrating the range of analyte concentration values within each WI/PWL segments from both mainstem and tributaries, are included below.")}`
`r if(grouping_for_chem=="site"){paste("Plots illustrating the range of analyte concentration values for each site are included below.")}` `r if(limit_to_nuts){paste("Analytes selected for presentation were subset to those of specific interest to the study and include nitrate, nitrate + nitrite (as N), nitrite (as N), total nitrogen, ammonia, total kjeldahl nitrogen (TKN), total phosphorus, and turbidity, and in-situ parameters: dissolved oxygen, temperature, pH, and specific conductance.")}` 
`r if(nrow(temp5>0)){paste("Excursions are indicated by an asterisk. Site specific excursions are quantified in Section II.")}`

```{r echo=FALSE, message=FALSE, warning=FALSE}
#source(here::here(),
     #  "r_scripts_raw",
    #   "stayCALM_violations.R")

```

<!---BLOCK_LANDSCAPE_START--->
```{r tab.id= "Analytes", echo=FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(flextable)

# tl.1<-flextable(analyte_final) %>% 
#   font(i = NULL, j = NULL, fontname="Arial", part = "all") %>% 
#   theme_zebra() %>% 
#   fontsize(size = 8, part="all")%>%
#   autofit()
# tl.1<-align(tl.1, i = NULL, j =(2:10) , align = "center", part = "all")%>%
#   width(j=c(6:10), width = 0.8)%>%
#   width(j=3:5, width=0.6)%>%
#   width(j=1, width=1.2)
 tl.1<-table.f(analyte_final,2,max(ncol(analyte_final)))
tl.1<-flextable::set_caption(tl.1,caption=("Water chemistry analytes sampled as part of the Stream Assessment Survey. Table lists sampled analytes and analytical specifications."),style="Table Caption",autonum = officer::run_autonum(seq_id = "tab",prop=officer::fp_text_lite(bold = FALSE)))
tl.1<-flextable::footnote(tl.1,ref_symbols =c("",""),part="header",value = as_paragraph(c("^ Precision objectives are defined by results of duplicate samples as described in SOP #102-20, and #110-21.","~ Not Applicable")))
tl.1

```
<!---BLOCK_LANDSCAPE_STOP--->

```{r include=FALSE,message=FALSE,warning=FALSE}

#load libraries
library(stringr)
library(reshape2)
library(ggplot2)
library(ggthemes)
library(pander)
library(dplyr)
library(forcats)

#set group colors
sites<-sites %>% 
  arrange(order)

#sites$group<-levels(with(sites,reorder(group,order)))
sites$group<-as.character(sites$group)
  
groups<-as.character(unique(sites$group))

group_colors <- setNames(RColorBrewer::brewer.pal(length(unique(sites$group)), "Set1"), levels(length(unique(sites$group))))

names(group_colors)<-c(groups)

group_colors <- group_colors[!is.na(names(group_colors))] 

#group_colors<-c("downstream"= "tomato2", "upstream"= "springgreen4")#, "c"="deepskyblue2")
#group_colors<-c("a"= "tomato2", "b"= "springgreen4", "c"="deepskyblue2")
chem.trans<-chem.trans %>% 
  arrange(CHEM_PARAMETER_NAME)
```


```{r chemgraph1, echo=FALSE, fig.width=7, fig.height=6,fig.align='center', message=FALSE, warning=FALSE, fig.cap=paste(unique(chem.trans$CHEM_PARAMETER_NAME), ", " , label, sep="")}
  

if(nrow(chem.trans)>1 & grouping_for_chem=="site"){

    label="Stars at the bottom of the graph indicate a violation of a WQS (if applicable). Axis are presented in log scale for comparison.The total number of reported values illustrated for each sampling location can vary due to non-detection and QA/QC procedures.Color corresponds to watershed group indicated in legend. Yellow dots (if included) indicate samples taken at event flow rates."
chem.graph.site(chem.trans)
    }

if(nrow(chem.trans)>1 & grouping_for_chem=="PWL"){
    label="Stars at the bottom of the graph indicate a violation of a WQS (if applicable). Axis are presented in log scale for comparison.The total number of reported values illustrated for each sampling location can vary due to non-detection and QA/QC procedures. Color corresponds to watershed group indicated in legend. Yellow dots (if included) indicate samples taken at event flow rates."
 
  chem.graph.pwl(chem.trans)
 
}


```


```{r turb, echo=FALSE, fig.width=7, fig.height=6, fig.align='center',message=FALSE, warning=FALSE, fig.cap=paste(unique(chem.no.trans$CHEM_PARAMETER_NAME), ", " , label, sep="")}

#this one for the other values (no transformation of units-in situ data)
 
if (nrow(chem.no.trans)>0 & grouping_for_chem=="site"){
  chem.graph.continuous.site(chem.no.trans)
}


if (nrow(chem.no.trans)>0 & grouping_for_chem=="PWL"){
  chem.graph.continuous.pwl(chem.no.trans)
}
```



```{r insituChem, echo=FALSE, fig.width=7, fig.height=6, fig.align='center',message=FALSE, warning=FALSE, fig.cap=paste(unique(in.situ.short$CHEM_PARAMETER_NAME), ", " , label, sep="")}

#this one for the other values (no transformation of units-in situ data)
 


if (nrow(in.situ.short)>0 & grouping_for_chem=="site"){
  chem.graph.insitu.site(in.situ.short)
}

if (nrow(in.situ.short)>0 & grouping_for_chem=="PWL"){
  chem.graph.insitu.pwl(in.situ.short)
}


```



